### 2016-09-30 features.tex
Define "bedrock areas"

Although SymPy's extensive feature set cannot be covered in depth in this
paper, calculus and other bedrock areas are discussed in their own
subsections. Additionally, Table~\ref{features-table} gives a compact listing
of all major capabilities present in the SymPy codebase. This grants a
sampling from the breadth of topics and application domains that SymPy
services. Unless stated otherwise, all features noted in
Table~\ref{features-table} are symbolic in nature. Numeric features are
discussed in Section~\ref{sec:numerics}.

>>>>

Although SymPy's extensive feature set cannot be covered in depth in this
paper, bedrock areas, that is, those areas that are used throughout the
library, are discussed in their own
subsections below. Additionally, Table~\ref{features-table} gives a compact listing
of all major capabilities present in the SymPy codebase. This grants a
sampling from the breadth of topics and application domains that SymPy
services. Unless stated otherwise, all features noted in
Table~\ref{features-table} are symbolic in nature. Numeric features are
discussed in Section~\ref{sec:numerics}.
